Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-21 Manuscript/Manuscript.Rmd
Draft of intro ready (needs trimming though)

(current, 708 words. Aim for 650)

  The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016). Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007). However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction (de la Vega et al., 2016). Focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight multifaceted representations of psychological constructs within mPFC subregions. However, recent activation-based meta-analytic has demonstrated domain specificity in this area (Kragel et al., 2018). In addition, coordinate-based meta-analyses rely on peak coordinates derived from group-averaged data. It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret. Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. For example, Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks. Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses. Importantly, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present in mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. A popular approach is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix), and the resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). This method could thus highlight the cluster of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making. We do this by capitalizing on therespective strengths of meta-analytic and subject-specific analyses of brain data.

>>>>

(Current: 880 words. Aim for 650)

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007). However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016). More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018). While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying overall trends in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in agglomerative estimations (Laumann....; Gordon et al., 2018). Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018). In regards to DMN, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2018, Tobyne et al., 2018). A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018). From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). This method could thus highlight a refined cluster of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature according to an established brain atlas (Glasser et al., 2013). We then produce a network of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection. We finalize by quantifying the generazibility and stability of the resulting functional topologies across subjects, and compare the approach to more traditional seed-based correlation methods.
